The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources

### 2019-12-18 paper.tex
Updated equation 27 to include radiative efficiency factor epsilon.

The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
\begin{equation}
    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
\end{equation}
where M is black hole mass, G is the gravitational constant, and v is the black hole velocity.

>>>>

The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
\begin{equation}
    \dot{M}_{acc} = \epsilon\frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
\end{equation}
where $\epsilon$ is the radiative efficiency as calculated in Equation 13 of \citet{2019MNRAS.486.5377I}, M is black hole mass, G is the gravitational constant, and v is the black hole velocity.
